Comparison of Log Likelihood Values

### 2017-08-02 R/LogLikelihood_Comparison.Rmd
I went back to double check my tables of log likelihood values to make sure I hadn't entered anything incorrectly. As it turns out, I accidentally printed the physical activity models to htmlreg twice, which explains why the physical activity and mental health likelihood values were the same after adding park access into the models. I fixed the problem and added the correct values to the tables.
I removed the Northeastern census tract from Denver and also removed a handfull of census tracts from Boston that comprised mostly null values. As expected, the log likelihood values changed in Denver

---
title: "Comparison of Log Likelihood Values"
author: "Nico Boyd"
date: "June 19, 2017"
output:
  html_document: default
---

@@

@@

  * Denver: models 1 & 4 (both equally likely)
  * Boston: models 3 & 6 (both equally likely)
  * NYC: models 1 & 2 (both equally likely)

```{r denver_models, echo=FALSE}

Denver_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
Denver_Loglikelihoods[,1] <- c(-184.46, -184.46, -184.46, -184.46, -184.46, -184.46)
Denver_Loglikelihoods[,2] <- c(-218.96, -218.96, -218.96, -218.96, -218.96, -218.96)
Denver_Loglikelihoods[,3] <- c(-218.96, -218.96, -218.96, -218.96, -218.96, -218.96)
Denver_Loglikelihoods[,4] <- c(-184.39, -184.43, -184.43, -184.39, -184.43, -184.43)
Denver_Loglikelihoods[,5] <- c(-218.06, -218.28, -218.31, -218.06, -218.28, -218.31)
Denver_Loglikelihoods[,6] <- c(-218.06, -218.28, -218.31, -218.06, -218.28, -218.31)
colnames(Denver_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Denver_Loglikelihoods
```

```{r boston_models, echo=FALSE}

Boston_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
Boston_Loglikelihoods[,1] <- c(-258.16, -258.16, -258.16, -258.16, -258.16, -258.16)
Boston_Loglikelihoods[,2] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
Boston_Loglikelihoods[,3] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
Boston_Loglikelihoods[,4] <- c(-258.16, -258.16, -258.15, -258.16, -258.16, -258.15)
Boston_Loglikelihoods[,5] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
Boston_Loglikelihoods[,6] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
colnames(Boston_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Boston_Loglikelihoods
```

```{r nyc_models, echo=FALSE}

NYC_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
NYC_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
NYC_Loglikelihoods[,3] <- c(-4421.83, -4421.83, -4421.83)
NYC_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
NYC_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
NYC_Loglikelihoods[,6] <- c(-4421.80, -4421.80, -4421.82)
colnames(NYC_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

NYC_Loglikelihoods
```

>>>>

---
title: "Comparison of Log Likelihood Values"
author: "Nico Boyd"
date: "August 1, 2017"
output:
  html_document: default
---

@@

  > It's more odd that the log-likelihoods are the same for both model before
  the park access is added. Are you sure you didn't copy the wrong values/use the
  wrong formula?

  > *I went ahead and removed the large Northeastern census tract from Denver and also removed a handful of tracts      from Boston that comprised mostly null values. I re-ran the models and double checked myself but sure enough, the     log-likelihoods were the same for each set of models before adding park access. I discovered that the reason the log   likelihood values were the same for the physical activity and mental health models after adding park access was       that I had accidentally printed the physical activity model to htmlreg twice, so I fixed that problem and updated my   tables with the correct values. The results are less straightforward than what we saw before; see my notes below on   which models are most likely for each city and dependent variable.*

@@

  > That's right; pick the least negative value.

  * Denver: SEM models 1 & 4 are most likely (both equally so) for physical activity and mental health, but least         likely for obesity; SEM models 2 & 3 are tied for most likely for obesity. The same is true of the SDM models.

  * Boston: SEM models 3 & 6 remain the most likely for all three dependent variables. However, for the SDM models, 1     & 3 are the most likely for all three variables.

  * NYC: SEM models 1 & 2 are most likely for obesity and physical activity, while all three models are equally likely     for mental health. For the SDM models, model 3 is most likely for physical activity and mental health, but Model 1     is most likely for obesity.

### Denver SEM Models
Models 1 and 4 are the most likely (both equally so) for physical activity and mental health, but least likely for obesity.
```{r denver_SEM_models, echo=FALSE}

Denver_SEM_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
Denver_SEM_Loglikelihoods[,1] <- c(-183.33, -183.33, -183.33, -183.33, -183.33, -183.33)
Denver_SEM_Loglikelihoods[,2] <- c(-216.98, -216.98, -216.98, -216.98, -216.98, -216.98)
Denver_SEM_Loglikelihoods[,3] <- c(-134.84, -134.84, -134.84, -134.84, -134.84, -134.84)
Denver_SEM_Loglikelihoods[,4] <- c(-183.16, -183.06, -183.06, -183.16, -183.06, -183.06)
Denver_SEM_Loglikelihoods[,5] <- c(-216.86, -216.96, -216.97, -216.86, -216.96, -216.97)
Denver_SEM_Loglikelihoods[,6] <- c(-134.67, -134.84, -134.84, -134.67, -134.84, -134.84)
colnames(Denver_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Denver_SEM_Loglikelihoods
```

### Denver SDM Models
Models 1 and 4 are most likely (both equally so) for physical activity and mental health, but least likely for obesity.
```{r denver_SDM_models, echo=FALSE}

Denver_SDM_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
Denver_SDM_Loglikelihoods[,1] <- c(-158.89, -158.89, -158.89, -158.89, -158.89, -158.89)
Denver_SDM_Loglikelihoods[,2] <- c(-188.72, -188.72, -188.72, -188.72, -188.72, -188.72)
Denver_SDM_Loglikelihoods[,3] <- c(-120.84, -120.84, -120.84, -120.84, -120.84, -120.84)
Denver_SDM_Loglikelihoods[,4] <- c(-157.99, -158.54, -158.56, -157.99, -158.55, -158.56)
Denver_SDM_Loglikelihoods[,5] <- c(-185.17, -185.29, -185.34, -185.17, -185.30, -185.34)
Denver_SDM_Loglikelihoods[,6] <- c(-120.23, -120.64, -120.66, -120.23, -120.64, -120.66)
colnames(Denver_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Denver_SDM_Loglikelihoods
```

### Boston SEM Models
Models 3 and 6 are most likely for all three dependent variables.
```{r boston_SEM_models, echo=FALSE}

Boston_SEM_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
Boston_SEM_Loglikelihoods[,1] <- c(-258.16, -258.16, -258.16, -258.16, -258.16, -258.16)
Boston_SEM_Loglikelihoods[,2] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
Boston_SEM_Loglikelihoods[,3] <- c(-211.45, -211.45, -211.45, -211.45, -211.45, -211.45)
Boston_SEM_Loglikelihoods[,4] <- c(-258.16, -258.16, -258.15, -258.16, -258.16, -258.15)
Boston_SEM_Loglikelihoods[,5] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
Boston_SEM_Loglikelihoods[,6] <- c(-211.44, -211.43, -211.36, -211.44, -211.43, -211.36)
colnames(Boston_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Boston_SEM_Loglikelihoods
```

### Boston SDM Models
Models 1 and 3 are most likely for all three dependent variables.
```{r boston_SDM_models, echo=FALSE}

Boston_SDM_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
Boston_SDM_Loglikelihoods[,1] <- c(-230.37, -230.37, -230.37, -230.37, -230.37, -230.37)
Boston_SDM_Loglikelihoods[,2] <- c(-298.10, -298.10, -298.10, -298.10, -298.10, -298.10)
Boston_SDM_Loglikelihoods[,3] <- c(-198.01, -198.01, -198.01, -198.01, -198.01, -198.01)
Boston_SDM_Loglikelihoods[,4] <- c(-228.51, -229.42, -229.87, -228.51, -229.42, -229.87)
Boston_SDM_Loglikelihoods[,5] <- c(-297.21, -297.55, -297.73, -297.21, -297.55, -297.73)
Boston_SDM_Loglikelihoods[,6] <- c(-197.19, -197.91, -197.74, -197.20, -197.91, -197.74)
colnames(Boston_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Boston_SDM_Loglikelihoods
```

### NYC SEM Models
Models 1 and 2 are most likely (both equally so) for obesity and physical activity. All three models are equally likely for mental health.
```{r nyc_SEM_models, echo=FALSE}

NYC_SEM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_SEM_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
NYC_SEM_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
NYC_SEM_Loglikelihoods[,3] <- c(-2716.36, -2716.36, -2716.36)
NYC_SEM_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
NYC_SEM_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
NYC_SEM_Loglikelihoods[,6] <- c(-2716.33, -2716.33, -2716.33)
colnames(NYC_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

NYC_SEM_Loglikelihoods
```

### NYC SDM Models
Model 3 is most likely for physical activity and mental health, but Model 1 is most likely for obesity.
```{r nyc_SDM_models, echo=FALSE}

NYC_SDM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_SDM_Loglikelihoods[,1] <- c(-3819.95, -3819.95, -3819.95)
NYC_SDM_Loglikelihoods[,2] <- c(-4369.45, -4369.45, -4369.45)
NYC_SDM_Loglikelihoods[,3] <- c(-2656.60, -2656.60, -2656.60)
NYC_SDM_Loglikelihoods[,4] <- c(-3808.52, -3808.53, -3812.65)
NYC_SDM_Loglikelihoods[,5] <- c(-4368.97, -4368.96, -4368.45)
NYC_SDM_Loglikelihoods[,6] <- c(-2655.48, -2655.48, -2655.36)
colnames(NYC_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

NYC_SDM_Loglikelihoods
```
